Wiggling the bandwidth

### 2023-01-28 paper.tex
add range experiments and evaluation

\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\argmin}{argmin}

@@

>>>>

\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\Te}{Te}
\DeclareMathOperator{\argmin}{argmin}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=\textwidth]{range}
    \caption{
        Standard versus wiggled estimators. 
        The green vertical line shows the base bandwidth.
        The dots indicate the minima.
        The blue line is indepdent of the base bandwidth. }
    \label{fig:range}
\end{figure}

In this first experiment we want to find out the relationship between wiggled
estimator $\hat f_{\gamma_0,\gamma}$ and standard estimator 
$\hat f_{\gamma,\gamma}$.
We choose a reasonably hard function $[3/2, 3] \to \R$, namely
\[ f(x) = \zeta(x) \sin(20 x), \]
and pick $N_{\Tr} = 30$ uniformly sampled training points.
In a range of $\Gamma = [10,50]$ we plot the performance on 
a training set (regular grid, $N_{\Te} = 1000$) of the "standard" estimator
for each $\gamma$ and the "wiggled" estimator wiggled for the same 
$\gamma$ but previously fit on a fixed base bandwidth $\gamma_0$.
We plot this 6 times for different base bandwidth.
See \cref{fig:range} for the results.

We summarize the observations:
\begin{itemize}
    \item Generally, the behavior of wiggling $\gamma$ away from $\gamma_0$
        is smooth as expected.
    \item The first four plots show that wiggling improves over standard
        estimators even if the base bandwidth is already optimal.
    \item If the base bandwidth is chosen too small, then a iterated 
        wiggle search goes in the direction of the standard optimal bandwidth.
    \item However, plot no. 5 shows that this seems not be the case in general.
\end{itemize}
